Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
improve section 'Program synthesis for the example'

This candidate solution is validated as the final solution by both stages
{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.

@@

Figure~\ref{fig:bode} shows the Bode diagram of the closed-loop system from~\cite{DBLP:conf/hybrid/WangGRJF16} 
(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
The phase margin in Figure~\ref{fig:original} is negative, which means that the controller 
from~\cite{DBLP:conf/hybrid/WangGRJF16} is unstable, considering FWL effects. 
Note that the final solution from \tool is stable since it presents an infinite phase margin 
and a gain margin of $17.8 dB$.
%
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}.}
        \label{fig:original}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
        \caption{Controller synthesised by \tool.}
        \label{fig:cegiscontroller}
    \end{subfigure}
    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesised closed-loop systems.}\label{fig:bode}
\end{figure}

>>>>

This candidate solution is validated as the final solution by both stages
{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
In particular, Figure~\ref{fig:bode} shows the Bode diagram of the closed-loop system from~\cite{DBLP:conf/hybrid/WangGRJF16} 
(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}).

@@

The phase margin in Figure~\ref{fig:original} is negative, which means that the controller 
from~\cite{DBLP:conf/hybrid/WangGRJF16} is unstable, considering FWL effects. 
Note that the final solution from \tool is stable since it presents an infinite phase margin 
and a gain margin of $17.8 dB$.
%
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}.}
        \label{fig:original}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
        \caption{Controller synthesised by \tool.}
        \label{fig:cegiscontroller}
    \end{subfigure}
    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesised closed-loop systems.}\label{fig:bode}
\end{figure}
